Finite element analysis ofmulti-dimensional and simplifiedmodels for beams and plates

### 2023-11-07 files/Chapter1/PlateModel.tex
symbols

	Any point on the plate can be described by
	\[ \bar{x} = x_1 \bar e_1 + x_2 \bar e_2 + x_3 \bar e_3 = q \bar e_r + x_3 \bar e_3. \]

@@

	\subsubsection*{Equations of Motion}\label{sssec:P_Model:EquationsOfMotion}
	\begin{eqnarray}
		\rho h \partial_t^2 w & = & \textrm{div} Q + q \label{eq:P_Model:EM1}\\
		\rho I \partial_t^2 {\psi} & = & \textrm{div} M - Q \label{P2}\label{eq:P_Model:EM1}
	\end{eqnarray}
	In these equations $\rho$ denotes the density of the plate, $\displaystyle I = \frac{h^3}{12}$ the length moment of inertia, $M$ the moment density and $Q$ the shear force density. The parameter $q$ is an external force acting on the plate. The moment density is defined as

@@

	\subsubsection*{Constitutive Equations}\label{sssec:P_Model:ConstitutiveEquation}
	For the linear model, the constitutive equations are defined as:
	\begin{eqnarray}
		Q & = & \kappa^2 G h(\nabla w + \psi) \label{eq:P_Model:CE1} \\
		M_{11} & = & \frac{1}{2} D \left[2(\partial_1 \psi_1 + \nu \partial_2 \psi_2)\right]  \label{eq:P_Model:CE2}\\
		M_{12} =  M_{21} & = & \frac{1}{2} D \left[(1-\nu)(\partial_1 \psi_2 + \nu \partial_2 \psi_2)\right] \label{eq:P_Model:CE3} \\
		M_{22} & = & \frac{1}{2} D \left[2(\partial_2 \psi_2 + \nu \partial_1 \psi_1)\right] \label{eq:P_Model:CE4}
	\end{eqnarray}
	where $G$ is the shear modulus, $\kappa^2$ a shear correction factor and $D$ is a measure of stiffness for the plate and is defined by
	\begin{eqnarray*}
		D & = & \frac{EI}{1-\nu^2}
	\end{eqnarray*}
	where $E$ is Young's modulus and $\nu$ Poisson's ratio.\\

	In classical plate theory, $\psi = -\nabla w$ and the constitutive equation for $Q$ is excluded.

@@

	\subsubsection{Dimensionless Equations of Motion}\label{sssec:P_Model:EquationsOfMotionD}
	\begin{eqnarray}
		h \partial_t^2 w & = & \textrm{div} Q + q \label{eq:P_Model:EM1D} \\
		I \partial_t^2 {\psi} & = & \textrm{div} M - Q \label{eq:P_Model:EM2D_chap1}
	\end{eqnarray}
	\subsubsection{Dimensionless Constitutive Equations}\label{sssec:P_Model:ConstitutiveEquationsD}
	\begin{eqnarray}
		Q & = & h(\nabla w + \psi) \label{eq:P_Model:CE1D}\\
		M_{11} & = & \frac{1}{2\beta(1-\nu^2)} \left[ 2(\partial_1\psi_1 + \nu \partial_2 \psi_2 \right] \label{eq:P_Model:CE2D}\\
		M_{12} = M_{21} & = & \frac{1}{2\beta(1-\nu^2)} \left[ (1-\nu)(\partial_1\psi_2 + \partial_2 \psi_1) \right] \label{eq:P_Model:CE3D}\\
		M_{11} & = & \frac{1}{2\beta(1-\nu^2)} \left[ 2(\partial_2 \psi_2 + \nu \partial_1 \psi_1)\right] \label{eq:P_Model:CE4D_chap1}
	\end{eqnarray}
	\subsection{Boundary Conditions}\label{ssec:P_Model:BoundaryConditions}
	The boundary conditions are applied along an edge of a plate. Let $n$ be the outward normal of the edge, and $\tau$ be a unit vector tangent to that edge.\\

@@

	Free Edge:
	\[Mn\cdot n = 0, \ \ Mn\cdot \tau = 0 \ \ \textrm{ and }\ Q\cdot n = 0 \]
	Soft Supported Edge:
	\[Mn\cdot n = 0, \ \ w = 0 \ \ \textrm{ and } \ Mn \cdot \tau = 0 \]
	Rigidly Supported Edge:
	\[Mn\cdot n = 0, \ \ w = 0 \ \ \textrm{ and } \ {\psi} \cdot \tau = 0 \]
	Soft Clamped Edge:
	\[w = 0, \ \ Mn \cdot \tau = 0 \ \ \textrm{ and } \ \psi \cdot n = 0 \]
	Rigidly Clamped Edge:
	\[w = 0, \ \ \psi_1 = 0 \ \ \textrm{ and } \ \psi_2 = 0 \]

@@

	Boundary Conditions\\
	\[w = 0,  \ \textrm{ and } \ \psi = \bar{0} \ \textrm{ on } \Sigma_0.\]
	\[Mn\cdot n = 0,\ \ \ Mn\cdot \tau = 0, \ \textrm{ and } \ Q \cdot n =0 \ \textrm{ on } \partial\Omega\setminus\Sigma_0.\]
	with $\tau$ a unit vector perpendicular to $n$.\\

@@

	\subsection{Variational Form}\label{ssec:P_Model:VariationalForm}
	Let $v \in C_2^1[0,1]$ and $w \in C^1[0,1] \times C^1[0,1]$ such that $w$ is a vector valued function. Multiplication these functions to \eqref{eq:P_Model:EM1D} and \eqref{eq:P_Model:EM2D} yields:
	\begin{eqnarray*}
		\int_\Omega h \partial_t^2 w v \ dA & = & \int_\Omega \textrm{div} (Q) v \ dA + \int_\Omega q v \ dA\\
		\int_\Omega I \partial_t^2 \psi \cdot \phi \ dA & = & \int_\Omega \textrm{div} (M) \cdot \phi \ dA - \int_\Omega Q \cdot \phi \ dA
	\end{eqnarray*}

	Following from Green's Formulas, similar to section \ref{ssec:3D_Model:VariationalForm}, 
	\begin{eqnarray*}
		\int_\Omega \textrm{div}(Q) v \ dA & = & - \int_\Omega Q \cdot \nabla v \ dA + \int_{\partial\Omega} (Q\cdot n)v ds,\\
		\int_\Omega \textrm{div}(M) \cdot \phi \ dA & = & - \int_\Omega \textrm{Tr} (M \Phi) \ dA + \int_{\partial\Omega} M n \cdot \phi ds.
	\end{eqnarray*}
	$\textrm{Tr} (M \Phi)$ is the trace of the matrix $M \Phi$, $n$ is the normal vector to $\Omega$, and 
	\begin{eqnarray*}
		\Phi = 
		\begin{bmatrix}
			\partial_1\phi_1 & \partial_2\phi_1\\
			\partial_1\phi_2 & \partial_2\phi_2
		\end{bmatrix}.
	\end{eqnarray*}

@@

	Using the test function space for Problem P-1, the equations \eqref{P1} and \eqref{P2} reduce to
	\begin{eqnarray}
		\int_\Omega h \partial_t^2 w v \ dA & = & - \int_\Omega Q \cdot \nabla v \ dA + \int_\Omega q v \ dA, \label{eq:P_Model:ProblemP1V1}\\
		\int_\Omega I \partial_t^2 \psi \cdot \phi \ dA & = & - b(\phi,v) - \int_\Omega Q \cdot \phi \ dA, \label{eq:P_Model:ProblemP1V2}
	\end{eqnarray}
	for all $v \in T_1(\bar{\Omega})$ and $\phi \in T_2(\bar{\Omega})$

	\subsubsection{Bilinear Forms and integral}\label{sssec:P_Model:BilinearForm}
	Let $u = \langle w, \psi \rangle$ and $\phi = \langle v, \phi \rangle$. Define the bilinear forms
	\begin{eqnarray*}
		b(u,\phi) & = & \int_\Omega Q \cdot \nabla v \ dA + \int_{\Omega} \textrm{Tr}(M\Phi) \ dA,
	\end{eqnarray*}
	and
	\begin{eqnarray}
		c(u,\phi) = \int_\Omega h (\partial_t^2 w) v \ dA + \int_\Omega I (\partial_t^2 \psi) \cdot \phi \ dA \label{eq:2D_Model:Bilinear_c}
	\end{eqnarray}
	Also define the integral
	\begin{eqnarray}
		(f,g) &=& -\int_{\Omega} f\cdot g \ dA \label{eq:2D_Model:Bilinear_int}
	\end{eqnarray}

>>>>

	Any point on the plate can be described by
	\[ \bar{x} = x_1 \bar e_1 + x_2 \bar e_2 + x_3 \bar e_3 = q \bar e_r + x_3 \bar e_3. \] \label{sym:en}

@@

	\subsubsection*{Equations of Motion}\label{sssec:P_Model:EquationsOfMotion}
	\begin{eqnarray}
		\rho h \partial_t^2 w & = & \textrm{div} \mathbf{Q} + q \label{eq:P_Model:EM1}\\
		\rho I \partial_t^2 {\psi} & = & \textrm{div} M - Q \label{P2}\label{eq:P_Model:EM1}
	\end{eqnarray} \label{sym:bfQ}
	In these equations $\rho$ denotes the density of the plate, $\displaystyle I = \frac{h^3}{12}$ the length moment of inertia, $M$ the moment density and $Q$ the shear force density. The parameter $q$ is an external force acting on the plate. The moment density is defined as

@@

	\subsubsection*{Constitutive Equations}\label{sssec:P_Model:ConstitutiveEquation}
	For the linear model, the constitutive equations are defined as:
	\begin{eqnarray}
		\mathbf{Q} & = & \kappa^2 G h(\nabla w + \psi) \label{eq:P_Model:CE1} \\
		M_{11} & = & \frac{1}{2} D \left[2(\partial_1 \psi_1 + \nu \partial_2 \psi_2)\right]  \label{eq:P_Model:CE2}\\
		M_{12} =  M_{21} & = & \frac{1}{2} D \left[(1-\nu)(\partial_1 \psi_2 + \nu \partial_2 \psi_2)\right] \label{eq:P_Model:CE3} \\
		M_{22} & = & \frac{1}{2} D \left[2(\partial_2 \psi_2 + \nu \partial_1 \psi_1)\right] \label{eq:P_Model:CE4}
	\end{eqnarray}
	where $G$ is the shear modulus, $\kappa^2$ a shear correction factor and $D$ is a measure of stiffness for the plate and is defined by
	\begin{eqnarray*}
		D & = & \frac{EI}{1-\nu^2}
	\end{eqnarray*}
	where $E$ is Young's modulus and $\nu$ Poisson's ratio.\\

	In classical plate theory, $\psi = -\nabla w$ and the constitutive equation for $\mathbf{Q}$ is excluded.

@@

	\subsubsection{Dimensionless Equations of Motion}\label{sssec:P_Model:EquationsOfMotionD}
	\begin{eqnarray}
		h \partial_t^2 w & = & \textrm{div} \mathbf{Q} + q \label{eq:P_Model:EM1D} \\
		I \partial_t^2 {\psi} & = & \textrm{div} M - Q \label{eq:P_Model:EM2D_chap1}
	\end{eqnarray}
	\subsubsection{Dimensionless Constitutive Equations}\label{sssec:P_Model:ConstitutiveEquationsD}
	\begin{eqnarray}
		\mathbf{Q} & = & h(\nabla w + \psi) \label{eq:P_Model:CE1D}\\
		M_{11} & = & \frac{1}{2\beta(1-\nu^2)} \left[ 2(\partial_1\psi_1 + \nu \partial_2 \psi_2 \right] \label{eq:P_Model:CE2D}\\
		M_{12} = M_{21} & = & \frac{1}{2\beta(1-\nu^2)} \left[ (1-\nu)(\partial_1\psi_2 + \partial_2 \psi_1) \right] \label{eq:P_Model:CE3D}\\
		M_{11} & = & \frac{1}{2\beta(1-\nu^2)} \left[ 2(\partial_2 \psi_2 + \nu \partial_1 \psi_1)\right] \label{eq:P_Model:CE4D_chap1}
	\end{eqnarray}
	\subsection{Boundary Conditions}\label{ssec:P_Model:BoundaryConditions}
	The boundary conditions are applied along an edge of a plate. Let $n$ be the outward normal of the edge, and $\tau$ be a unit vector tangent to that edge.\\

@@

	Free Edge:
	\[Mn\cdot n = 0, \ \ Mn\cdot \tau = 0 \ \ \textrm{ and }\ \mathbf{Q}\cdot n = 0 \]
	Soft Supported Edge:
	\[Mn\cdot n = 0, \ \ w = 0 \ \ \textrm{ and } \ Mn \cdot \tau = 0 \]
	Rigidly Supported Edge:
	\[Mn\cdot n = 0, \ \ w = 0 \ \ \textrm{ and } \ {\psi} \cdot \tau = 0 \]
	Soft Clamped Edge:
	\[w = 0, \ \ Mn \cdot \tau = 0 \ \ \textrm{ and } \ \psi \cdot n = 0 \]
	Rigidly Clamped Edge:
	\[w = 0, \ \ \psi_1 = 0 \ \ \textrm{ and } \ \psi_2 = 0 \]

@@

	Boundary Conditions\\
	\[w = 0,  \ \textrm{ and } \ \psi = \bar{0} \ \textrm{ on } \Sigma_0.\]
	\[Mn\cdot n = 0,\ \ \ Mn\cdot \tau = 0, \ \textrm{ and } \ \mathbf{Q} \cdot n =0 \ \textrm{ on } \partial\Omega\setminus\Sigma_0.\]
	with $\tau$ a unit vector perpendicular to $n$.\\

@@

	\subsection{Variational Form}\label{ssec:P_Model:VariationalForm}
	Let $v \in C_2^1[0,1]$ and $w \in C^1[0,1] \times C^1[0,1]$ such that $w$ is a vector valued function. Multiplication these functions to \eqref{eq:P_Model:EM1D} and \eqref{eq:P_Model:EM2D} yields:
	\begin{eqnarray*}
		\int_\Omega h \partial_t^2 w v \ dA & = & \int_\Omega \textrm{div} (\mathbf{Q}) v \ dA + \int_\Omega q v \ dA\\
		\int_\Omega I \partial_t^2 \psi \cdot \phi \ dA & = & \int_\Omega \textrm{div} (M) \cdot \phi \ dA - \int_\Omega Q \cdot \phi \ dA
	\end{eqnarray*}

	Following from Green's Formulas, similar to section \ref{ssec:3D_Model:VariationalForm}, 
	\begin{eqnarray*}
		\int_\Omega \textrm{div}(\mathbf{Q}) v \ dA & = & - \int_\Omega \mathbf{Q} \cdot \nabla v \ dA + \int_{\partial\Omega} (Q\cdot n)v ds,\\
		\int_\Omega \textrm{div}(M) \cdot \phi \ dA & = & - \int_\Omega \textrm{Tr} (M \Phi) \ dA + \int_{\partial\Omega} M n \cdot \phi ds.
	\end{eqnarray*}
	$\textrm{Tr} (M \Phi)$ is the trace of the matrix $M \Phi$, $n$ is the normal vector to $\Omega$, and 
	\begin{eqnarray*}
		\Phi = 
		\begin{bmatrix}
			\partial_1\phi_1 & \partial_2\phi_1\\
			\partial_1\phi_2 & \partial_2\phi_2
		\end{bmatrix}.
	\end{eqnarray*}

@@

	Using the test function space for Problem P-1, the equations \eqref{P1} and \eqref{P2} reduce to
	\begin{eqnarray}
		\int_\Omega h \partial_t^2 w v \ dA & = & - \int_\Omega \mathbf{Q} \cdot \nabla v \ dA + \int_\Omega q v \ dA, \label{eq:P_Model:ProblemP1V1}\\
		\int_\Omega I \partial_t^2 \psi \cdot \phi \ dA & = & - b(\phi,v) - \int_\Omega Q \cdot \phi \ dA, \label{eq:P_Model:ProblemP1V2}
	\end{eqnarray}
	for all $v \in T_1(\bar{\Omega})$ and $\phi \in T_2(\bar{\Omega})$

	\subsubsection{Bilinear Forms and integral}\label{sssec:P_Model:BilinearForm}
	Let $u = \langle w, \psi \rangle$ and $\phi = \langle v, \phi \rangle$. Define the bilinear forms
	\begin{eqnarray*}
		b(u,\phi) & = & \int_\Omega \mathbf{Q} \cdot \nabla v \ dA + \int_{\Omega} \textrm{Tr}(M\Phi) \ dA,
	\end{eqnarray*}
	and
	\begin{eqnarray}
		c(u,\phi) = \int_\Omega h (\partial_t^2 w) v \ dA + \int_\Omega I (\partial_t^2 \psi) \cdot \phi \ dA \label{eq:2D_Model:Bilinear_c}
	\end{eqnarray}
	Also define the integral
	\begin{eqnarray}
		(f,g) &=& -\int_{\Omega} f\cdot g \ dA \label{eq:2D_Model:Bilinear_int}
	\end{eqnarray}

### 2023-11-07 files/Chapter2/generalvibrationmodel.tex
symbols

\section{Introduction} \label{sec:existence}
The models in this dissertation concern vibration of elastic bodies. These type of models have a similar variational form as the wave equation and are called second order hyperbolic type problems. This chapter discusses theory for the existence and uniqueness of solutions for these type of problems. The theoretical basis for modal analysis is also presented.\\

In this chapter we consider the work done by the authors of \cite{VV02} and \cite{VS19}. In these articles the authors prove the existence and uniqueness of solutions for general second order hyperbolic type problems. The problems in Chapter 1 are examples. The article \cite{VV02} concerns the case of a symmetric bilinear form $b$. The article \cite{VS19} extends this work where $b$ need not be symmetric. The article \cite{VV02} is sufficient for the models of this dissertation, while \cite{VS19} is only used where the notation is more convenient and to gain more insight.\\

Before the general theory is discussed, a model is presented to be used as an example to show the application of the theory. The model is a cantilever Timoshenko beam, denoted by Problem T-2 in Section \ref{ssec:1D_Model:ModelProblems}.\\

In Section \ref{ssec:1D_Model:VariationalForm}, the variational problem for the pinned-pinned beam is derived. The derivation of the cantilever beam model is similar, with a different test function space. Recall the variational problem for the cantilever beam Problem T-2V, with the test function space $\displaystyle T[0,1] = F_1[0,1] \times F_1[0,1]$. To determine the solvability of the problem, the weak variational problem is considered first.\\

To obtain the weak variational form of Problem T-2V some preparation is required. A natural setting for the problem is the product space $L^2(0,1)\times L^2(0,1)$, denoted by $X$. The inner product for $L^2(0,1)$ yields the inner product $\displaystyle (x_1,y_1) + (x_2,y_2)$ for $X$. The idea is to replace the pair $\langle w , \phi \rangle$ by a function $u$ ``of time only" and values $u(t)$ in the space $X$.\\

@@

The Sobolev space $H^1(0,1)$ is all the functions in $L^2(0,1)$ with at least a first-order weak derivative. $H^1(0,1)$ is complete (see Appendix A).\\

@@

\subsection{The variational approach}\label{ssec:existence:VariationlApproach}
Let $V$, $W$ and $X$ be real Hilbert spaces such that $W$ is a linear subspace of $X$, and $V$ is a linear subspace of $W$, i.e. $V \subset W \subset X$.
\begin{itemize}
	\item[] X is the global space with inner product $(\cdot,\cdot)_X$ and the induced norm $||\cdot||_X$.
	\item[] W is the inertia space with inner product $(\cdot,\cdot)_W$ and the induced norm $||\cdot||_W$.
	\item[] V is the energy space with inner product $(\cdot,\cdot)_V$ and the induced norm $||\cdot||_V$.
\end{itemize}

@@

\subsubsection*{Problem GVar}\label{sssec:existence:ProblemGVar}
Given a function $f:J\rightarrow X$, find a function $u\in C(J,\ X)$ such that $u'$ is continuous at $0$ with respect to $\Vert \cdot \Vert_{W}$ and for each $t\in J,\ u(t)\in V,\ u'(t) \in V,\ u''(t)\in W$ and
\begin{eqnarray}
	c(u''(t),v)+a(u'(t),v)+b(u(t),v)= (f(t),v)_{X} \ \ \ \ \textrm{for each} \ v \in V, \label{eq:existence:ProblemGVar}
\end{eqnarray}
while $u(0)=u_{0},\ \ \ u'(0)=u_{1}$.\\

@@

\newtheorem{Thm3n}[Thmx]{Theorem}
\begin{Thm3n}[Strong Damping]
	If $a$ is positive definite on $V$, there exists a unique solution $u \in C^1([0,\infty),V)\cap C^2((0,\infty),W)$ for Problem GVar for any $u_0 \in V$, $u_1 \in W$ and any $f$ which is Lipschitz on $V$. If $f=0$, then $u \in C^1([0,\infty),V)\cap C^2([0,\infty),W)\cap C^\infty((0,\infty),V)$.
\end{Thm3n}

@@

Let $u \in C_0^\infty(0,1)$. Then $u(0) = u(1) = 0$ and therefore $u \in T(0,1)$ and $C_0^\infty(0,1) \subset T(0,1)$. Recall that $V(0,1)$ is the closure of $T(0,1)$ in $H^1(0,1)$. So it follows that $C_0^\infty(0,1) \subset V(0,1) \subset H^1(0,1)$. And since $C_0^\infty(0,1)$ is dense in $L_2(0,1)$, both $V(0,1)$ and $H^1(0,1)$ are dense in $L_2(0,1)$. Therefore $V(0,1)\times V(0,1)$ is dense in $X = L_2(0,1) \times L_2(0,1)$.\\

>>>>

\section{Introduction} \label{sec:existence}
The models in this dissertation concern vibration of elastic bodies. These type of models have a similar variational form as the wave equation and are called second order hyperbolic type problems. This chapter discusses theory for the existence and uniqueness of solutions for these type of problems. The theoretical basis for modal analysis is also presented.

In this chapter we consider the work done by the authors of \cite{VV02} and \cite{VS19}. In these articles the authors prove the existence and uniqueness of solutions for general second order hyperbolic type problems. The problems in Chapter 1 are examples. The article \cite{VV02} concerns the case of a symmetric bilinear form $b$. The article \cite{VS19} extends this work where $b$ need not be symmetric. The article \cite{VV02} is sufficient for the models of this dissertation, while \cite{VS19} is only used where the notation is more convenient and to gain more insight.

Before the general theory is discussed, a model is presented to be used as an example to show the application of the theory. The model is a cantilever Timoshenko beam, denoted by Problem T-2 in Section \ref{ssec:1D_Model:ModelProblems}.

In Section \ref{ssec:1D_Model:VariationalForm}, the variational problem for the pinned-pinned beam is derived. The derivation of the cantilever beam model is similar, with a different test function space. Recall the variational problem for the cantilever beam Problem T-2V, with the test function space $\displaystyle T[0,1] = F_1[0,1] \times F_1[0,1]$. To determine the solvability of the problem, the weak variational problem is considered first.

To obtain the weak variational form of Problem T-2V some preparation is required. A natural setting for the problem is the product space $L^2(0,1)\times L^2(0,1)$, denoted by $X$. The inner product for $L^2(0,1)$ yields the inner product $\displaystyle (x_1,y_1) + (x_2,y_2)$ for $X$. The idea is to replace the pair $\langle w , \phi \rangle$ by a function $u$ ``of time only" and values $u(t)$ in the space $X$. \label{sym:Ln}

@@

The Sobolev space $H^1(0,1)$ is all the functions in $L^2(0,1)$ with at least a first-order weak derivative. $H^1(0,1)$ is complete (see Appendix A).\label{sym:Hn}

@@

\subsection{The variational approach}\label{ssec:existence:VariationlApproach}
Let $V$, $W$ and $X$ be real Hilbert spaces such that $W$ is a linear subspace of $X$, and $V$ is a linear subspace of $W$, i.e. $V \subset W \subset X$.
\begin{itemize}
	\item[] X is the global space with inner product $(\cdot,\cdot)_X$ and the induced norm $||\cdot||_X$.
	\item[] W is the inertia space with inner product $(\cdot,\cdot)_W$ and the induced norm $||\cdot||_W$.
	\item[] V is the energy space with inner product $(\cdot,\cdot)_V$ and the induced norm $||\cdot||_V$.
\end{itemize} \label{sym:Xspace}\label{sym:Wspace}\label{sym:Vspace}\label{sym:norm}

@@

\subsubsection*{Problem GVar}\label{sssec:existence:ProblemGVar}
Given a function $f:J\rightarrow X$, find a function $u\in C(J,\ X)$ such that $u'$ is continuous at $0$ with respect to $\Vert \cdot \Vert_{W}$ and for each $t\in J,\ u(t)\in V,\ u'(t) \in V,\ u''(t)\in W$ and
\begin{eqnarray}
	c(u''(t),v)+a(u'(t),v)+b(u(t),v)= (f(t),v)_{X} \ \ \ \ \textrm{for each} \ v \in V, \label{eq:existence:ProblemGVar}
\end{eqnarray}
while $u(0)=u_{0},\ \ \ u'(0)=u_{1}$.\label{sym:a} \\

@@

\newtheorem{Thm3n}[Thmx]{Theorem}
\begin{Thm3n}[Strong Damping]
	If $a$ is positive definite on $V$, there exists a unique solution $u \in C^1([0,\infty),V)\cap C^2((0,\infty),W)$ for Problem GVar for any $u_0 \in V$, $u_1 \in W$ and any $f$ which is Lipschitz on $V$. If $f=0$, then $u \in C^1([0,\infty),V)\cap C^2([0,\infty),W)\cap C^\infty((0,\infty),V)$.
\end{Thm3n} \label{Cinfty}

@@

Let $u \in C_0^\infty(0,1)$. Then $u(0) = u(1) = 0$ and therefore $u \in T(0,1)$ and $C_0^\infty(0,1) \subset T(0,1)$. Recall that $V(0,1)$ is the closure of $T(0,1)$ in $H^1(0,1)$. So it follows that $C_0^\infty(0,1) \subset V(0,1) \subset H^1(0,1)$. And since $C_0^\infty(0,1)$ is dense in $L_2(0,1)$, both $V(0,1)$ and $H^1(0,1)$ are dense in $L_2(0,1)$. Therefore $V(0,1)\times V(0,1)$ is dense in $X = L_2(0,1) \times L_2(0,1)$.\label{sym:Cinftyzero} \\

### 2023-11-07 files/Chapter6/Validity_Timo.tex
symbols

In this section, the validity of the Timoshenko beam model is investigated. Specifically, the validity of a cantilever Timoshenko beam model, using a cantilever two-dimensional beam model as a reference. This is a discussion and a replication of numerical results of the work done in the article \cite{LVV09}.

The article \cite{LVV09} is titled `Comparison of linear beam theories'. In this article, the authors compare a cantilever Timoshenko beam to a cantilever two-dimensional beam. \textcolor{red}{Give a brief summary of the article here, linking to whatever has already been discussed in the literature review.}

\subsection{The models}
The following two models are the focus of this section and the models that are used in the article \cite{LVV09}. From section \ref{ssec:1D_Model:ModelProblems}, the cantilever Timoshenko beam model, referred to as Problem T-2. From section \ref{ssec:2D_Model:ModelProblem}, the cantilever two-dimensional beam model, referred to as Problem 2D-1.\\

@@

\subsection{Calculating the eigenvalues and eigenvectors}
In section \ref{sec:Timo:EigenvalueProblem} a method for calculating the eigenvalues and eigenvectors of the Timoshenko beam is provided. And in section \ref{sec:Timo:Cantilever}, the eigenvalues and eigenvectors of a cantilever Timoshenko beam are calculated as an example. These can also be obtained to a desired level of accuracy.

@@

In this form, the eigenvalue problem is a system of ordinary differential equations, and can be solved using a numerical method.

>>>>

In this section, the validity of the Timoshenko beam model is investigated. Specifically, the validity of a cantilever Timoshenko beam model, using a cantilever two-dimensional beam model as a reference. This follows what is done in the article \cite{LVV09}. This section discusses the results of the article, focussing on the numerical results. Some of the results are replicated with more significant digits, others are extended to be used in the rest of this chapter.

The article \cite{LVV09} is titled `Comparison of linear beam theories'. In this article, the authors compare a cantilever Timoshenko beam to a cantilever two-dimensional beam. The authors start by presenting the models. These are the same as Problem T-2 and Problem 2D-1 that are defined in Chapter 1. The authors also look at the existence and uniqueness of the models, which is covered in Chapter 2 of this dissertation. The authors then calculate and compare the eigenvalues and eigenfunctions, which will be discussed in this section.

\subsection{The models}
The cantilever Timoshenko beam model is defined in section \ref{ssec:1D_Model:ModelProblems}, and is referred to as Problem T-2. The cantilever two-dimensional beam model is defined in section \ref{ssec:2D_Model:ModelProblem}, and is referred to as Problem 2D-1.

@@

\subsection{Calculating the eigenvalues and eigenvectors}
In section \ref{sec:Timo:EigenvalueProblem} a method for calculating the eigenvalues and eigenvectors of the Timoshenko beam is provided. And in section \ref{sec:Timo:Cantilever}, the eigenvalues and eigenvectors of a cantilever Timoshenko beam are calculated as an example.

@@

In this form, the eigenvalue problem is a system of ordinary differential equations, and can be solved using a numerical method. Computer programs like MATLAB provide functions that are able to solve this.
